An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/arch.tex
config: arch

\para{Learning.}
The input of the learner is a set of files that have been translated
into a well-structured representations of a list of keyword-value pairs (\ie, the translator's
outputs). The learner module employs a collection of learning algorithms
to generate various rules and constraints,
potentially used to handle different types of configuration errors.
These rules and constraints are the outputs of the learner, 
and will be used by the checker to detect errors later.
By combining the translated representations and the learned
rules together, we build a language model for
configuration verifications.
Because the translator outputs probabilistic typed entries,
the learner is responsible for determining a type for each entry.

Different from previous efforts, \eg, EnCore~\cite{zhang14encore},
which needs users or developers to provide explicit templates,
\app's learner encodes some predefined error-patterns 
to generate rules. 
As an illustration of a simple rule that we can learn,
consider an encoded pattern $X_1 \le X_2$, where $X_1$ and $X_2$ are
integer variables. The learner may derive the rule stating that
$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$. 
There is a classification and taxonomy of configuration errors in the 
existing work on automated configuration troubleshooting%
~\cite{yin11anempirical, configdataset}. 
Each class can be viewed as an error-pattern 
that \app should handle: we consider integer constraints, 
ordering errors, typing errors, correlation errors, etc.

>>>>

\para{Learning.}
The input of the learner is a set of files that have been translated
into well-structured representations (\ie, the translator's
outputs). The learner module employs a collection of learning algorithms
to generate various rules and constraints,
potentially used to handle different types of configuration errors.
These rules and constraints are the outputs of the learner, 
and will be used by the checker to detect errors later.
By combining the translated representations and the learned
rules together, we build a language model for
configuration verification.
Because the translator outputs probabilistically typed entries,
the learner is responsible for determining a type for each entry.

Different from previous efforts, \eg, EnCore~\cite{zhang14encore},
which requires users or developers to provide explicit templates,
\app's learner encodes some predefined error-patterns 
to generate rules. 
As an illustration of a simple rule that we can learn,
consider an encoded pattern $X_1 \le X_2$, where $X_1$ and $X_2$ are
integer variables. The learner may derive the rule stating that
$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$. 
There is a classification and taxonomy of configuration errors in the 
existing work on automated configuration troubleshooting%
~\cite{yin11anempirical, configdataset}. 
Each class can be viewed as an error-pattern 
that \app should handle: we consider integer constraints, 
ordering errors, typing errors, correlation errors, etc.
